Adaptive Disk Storage for Interaction Graphs

### 2014-04-24 notes/graph-adapt/main.tex
another pass at query i/o

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}(B)) = |\mathcal{P}(B)|\cdot\left(1-\frac{\sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}

@@

>>>>

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}(B)) = |\mathcal{P}(B)|\cdot\left(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}

@@

\subsection{Query I/0}

We are also given a function $f$ that maps a query to the frequency the
query is executed during a particular time range $[t_s,t_e]$:
$$
f:  \text{query} \rightarrow \text{time} * \text{time} \rightarrow \text{frequency}
$$

\noindent 
We are also given a function $m$ that maps a query to the set of sub-blocks that are
accessed to satisfy that query during a particular time range. 
$$
m:  \text{query} \rightarrow \text{time} * \text{time} \rightarrow \text{block set}
$$

\noindent Define:
$$
\bigcup_{B'\in m(q, q.t_s, q.t_e)} B'.A = M
$$

\noindent 
Generalizing, I think we want an equation like the following:
$$
L(\mathcal{P}(B)) = \sum_{q\in Q} \left( f(q, q.t_s, q.t_e) \cdot \left( \sum_{a \in M}
  s(a) + \left\vert{m(q, q.t_s, q.t_e)}\right\vert \cdot c(B)\right) \right)
$$
